\section{Project Objectives}

These were the proposed objectives for this funding period:

\begin{description}
    \item[3-Month] Deliverables
        \begin{enumerate}
            \item Recommended VE analysis / reporting method and metrics. 
            \item Validate methods and metrics using the simulations and apply
                to the phantom and potential human data.
        \end{enumerate}

    \item[6-Month] Deliverables
        \begin{enumerate}
            \item Create simulation data matching the Phase II phantom and a
                variety of focal configurations.
            \item Upload simulation data to QIDW\@.
        \end{enumerate}

    \item[12-Month] Deliverables
        \begin{enumerate}
            \item Test and analyze Phase II phantom samples as CIRS/UWM iterate
                on phantom recipes and determine the “best” recipe for
                viscoelastic phantom fabrication and distribution.
            \item Determine the ``best'' viscoelastic material models and
                constants to match the Phase II phantoms and human liver data.
            \item Provide validated open-source alternatives to commercial FEA
                packages. Benchmark results for phase II phantoms will be
                documented and supplied as an integral part of the open-source
                alternatives.
        \end{enumerate}

\end{description}

We have completed all of these objectives, as are detailed in the following
sections.  Section~\ref{sect:ve_analysis} reviews the empirical metrics that
were used to characterize the VE materials used for the Phase II phantom
studies, which were then compared with the human data.
Section~\ref{sect:digital_phantoms} describes the elastic and viscoelastic
digital phantom configuration that were developed, validated and uploaded to
the RSNA QIDW\@.  Section~\ref{sect:open_source} details the open-source numerical
solvers that were studied as alternative to the commercial solvers used in
Section~\ref{sect:digital_phantoms}, and finally Section~\ref{sect:future_work}
outlines the future efforts for this project in Round V funding.
